Ultrafast Electron Microscopes: Design Criteria, Electron Sources, and Column Modeling

### 2013-05-22 inc/model_results/compound/compound.tex
tweak model_results compound system section

Through the use of multiple electron optical components such as magnetic lenses and RF cavities and accelerators (properly region-of-influence limited by application of \ref{eq:reg_of_influence}), the extended AG model can be employed to design and assess a full UEM column from pulse generation to sample stage.
The design of such a compound system is, of course, a cornerstone of modern electron microscope development, although space-charge effects are generally not included, since, on average, there is usually no more than one electron in the microscope column at a time.
However, for a nanosecond DTEM~\cite{lagrange_nanosecond_2008,reed_evolution_2009}, the microscope column must be designed to compensate for transverse ($\smallT$) space-charge effects, which dominate the propagation dynamics for the prolate electron pulses employed in such instruments (see \ref{fig:compare_shape}).
For the ultrashort (i.e., picosecond and femtosecond) electron pulse durations used in UEMs~\cite{park_direct_2009} and UED experiments~\cite{oudheusden_electron_2007}, the longitudinal ($z$) pulse dynamics due to both dispersion and space-charge effects must also be considered (as indicated in \ref{fig:compare_shape}).

@@

\ref{fig:compound} shows an example of a compound element system for the delivery of an ultrashort electron pulse to the specimen area; in this case, optimized for $ N = 10^{ 6 } $ --- the number of electrons per pulse required for single shot diffraction measurements~\cite{armstrong_practical_2007}.
The displayed dynamics are for an electron pulse generated by a $\tau = $ 100fs $w = $ 0.1mm laser, driving a photocathode, with $\Delta E = $ 0.5eV, then accelerated by 20 kV to a velocity of $8.4 \times 10^{7} \text{m}/\text{s}$.
In this simple system, an optimum RF cavity ($ \Omega = \pi v_{{ \scriptscriptstyle 0}} / d $) is surrounded by two magnetic lenses (positioned a realistic 5cm to either side of the RF cavity) that compensate for the electron beam divergence due to the non-zero $ \eta_{\smallT} (0) $ and the negative spatial lensing of the RF pulse compression cavity.
For the transverse dimension, this arrangement of electron optical elements is similar to the Cooke triplet in optics.
The magnetic lenses are assumed to be identical and wired in series, and thus have equal magnetic field strengths.
The three lensing elements are positioned at a distance of 15cm from the cathode to the front of the first magnetic lens and are adjusted so as to space-time image the electron pulse 5cm behind the second magnetic lens.
The dependencies of the the spatial variances, $\sigma_{\alpha}$, shown in \ref{fig:compound} as the electron pulse propagates through the multi-element system, clearly illustrate the effect of the magnetic lenses and RF cavity in the transverse ($\smallT$) and longitudinal ($z$) dimensions.
As the image-to-object distance ratio is less than unity in this case, both the transverse and longitudinal imaged pulse dimensions are reduced relative to their initial values.

>>>>

Through the use of multiple electron optical components such as magnetic lenses, RF cavities, and accelerators (properly region-of-influence limited by application of \ref{eq:reg_of_influence}), the extended AG model can be employed to design and assess a full UEM column from pulse generation to sample stage.
The design of such a compound system is, of course, a cornerstone of modern electron microscope development, although space-charge effects are generally not included, since, on average, there is usually no more than one electron in the microscope column at a time.
However, for a nanosecond DTEM~\cite{lagrange_nanosecond_2008,reed_evolution_2009}, the microscope column must be designed to compensate for transverse ($\smallT$) space-charge effects, which dominate the propagation dynamics for the prolate electron pulses employed in such instruments (see \ref{fig:compare_shape}).
For the ultrashort (i.e., picosecond and femtosecond) electron pulse durations used in UEMs~\cite{park_direct_2009} and UED experiments~\cite{oudheusden_electron_2007}, the longitudinal ($z$) pulse dynamics due to both dispersion and space-charge effects must also be considered (as indicated in \ref{fig:compare_shape}).

@@

\ref{fig:compound} shows an example of a compound element system for the delivery of an ultrashort electron pulse to the specimen area; in this case, optimized for $ N = 10^{ 6 } $ --- the number of electrons per pulse required for single shot diffraction measurements~\cite{armstrong_practical_2007}.
The displayed dynamics are for an electron pulse generated by a laser having HW1/eM duration $\tau = $ 100fs and width $w = $ 0.1mm, driving a photocathode, with $\Delta E = $ 0.5eV, then accelerated by 20 kV to a velocity of $8.4 \times 10^{7} \text{m}/\text{s}$.
In this simple system, an optimum RF cavity ($ \Omega = \pi v_{{ \scriptscriptstyle 0}} / d $) is surrounded by two magnetic lenses (positioned a realistic 5cm to either side of the RF cavity) that compensate for the electron beam divergence due to the non-zero $ \eta_{\smallT} (0) $ and the negative spatial lensing of the RF pulse compression cavity.
For the transverse dimension, this arrangement of electron optical elements is similar to the Cooke triplet in optics.
The magnetic lenses are assumed to be identical and wired in series, and thus have equal magnetic field strengths.
The three lensing elements are positioned at a distance of 15cm from the cathode to the front of the first magnetic lens and are adjusted so as to space-time image the electron pulse 5cm behind the second magnetic lens.
The dependencies of the the spatial variances, $\sigma_{\alpha}$, shown in \ref{fig:compound} as the electron pulse propagates through the multi-element system, clearly illustrate the effect of the magnetic lenses and RF cavity in the transverse ($\smallT$) and longitudinal ($z$) dimensions.
As the image-to-object distance ratio is less than unity in this case, both the transverse and longitudinal imaged pulse dimensions are reduced relative to their initial values.
